%instrumentation
\section{Instrumentation}

For this project data will be acquired using accelerometers and force sensors. The accelerometer is provided through the use of the Shimmer3 device from ShimmerSensing. Force sensors are/might be from Interlink. %Data will be collected using MATLAB. 

The Shimmer3 device is a nine degree of freedom (DoF) Inertial Measurement Unit (IMU) possessing five different types of sensors; accelerometer, gyroscope, magnetometer and altimeter. The Shimmer3 is capable of being configured to enable or disable specific sensors depending on which is needed. For this project only the accelerometer module of the device will be used. The accelerometer in the Shimmer3 device is a LSM303DLHC. It has a three dimensional digital linear acceleration sensor with a range of \pm2g / \pm4g / \pm8g / \pm16g. \cite{LSM303DLHC} %It has 16bit data output and communicates through an I$^{2}$C serial interface. 
Communication between the Shimmer3 devices and the computer is through Bluetooth. The computer will be running MATLAB and the \textit{Shimmer MATLAB Instrument Driver Library} to collect the streamed data from the Shimmer3 device. 

The force sensors used in this project is from Interlink Electronics, models 402 and 406. The Force Sensing Resistor (FSR) 402 is a 13mm diameter circle single-zone resistor capable of force detection in a range from 20g to 2kg. The FSR 406 is similar but covers a larger area of 38mm in a square. \cite{IE400}
A total of six sensors will be used with three sensors under each foot. One FSR 406 is placed under the heel and two FSR 402 sensors are placed under the front of the foot at the left and right side of the anterior lateral eminence of the sole. One Arduino Nano will be placed at the back of the hip of the subject to handle data collection. Collected data will be stored on an SD card for later analysis with MATLAB. 
%[foot regions: https://www.sciencephoto.com/media/581111/view/anatomy-regions-of-the-right-foot]
%(https://www.digikey.ca/product-detail/en/interlink-electronics/30-73258/1027-1002-ND/2476470) big square sensor
%(https://www.digikey.ca/product-detail/en/interlink-electronics/30-81794/1027-1001-ND/2476468) small round sensor